SubsidyExplorer - Step 11: Final database of all pre-populated reform proposals

### 2022-09-20 scripts/11_final_proposal_database.Rmd
renaming

title: "SubsidyExplorer - Step 10: Final database of all pre-populated reform proposals"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
bibliography: "../pew-subsidies.bib"
---

@@

# Directories for the output files generated by this script
results_dir <- paste0(here::here("results", "10-final-database/"), folder_name)
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}
```

>>>>

title: "SubsidyExplorer - Step 11: Final database of all pre-populated reform proposals"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
bibliography: "../pew-subsidies.bib"
---

@@

# Directories for the output files generated by this script
results_dir <- paste0(here::here("results", "11-final-database/"), folder_name)
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}
```
